\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{geometry}
\geometry{top=2cm, bottom=2cm, left=2.5cm, right=2.5cm}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\title{The World of Ideal Forms as a Natural Phase of Cognitive Evolution: \\ Solving the Fermi Paradox Through GRA Nullification}
\author{Oleg Bitov}
\date{April 17, 2026}

\begin{document}

\maketitle

\begin{abstract}
This paper proposes an explanation of the Fermi Paradox based on the concept of \textbf{GRA Nullification} (Geometric Recursive Analytics). It is shown that any intelligent civilisation, during its evolution, inevitably constructs a \textit{world of ideal forms} (Platonic eide) using all types of GRA: static, cyclic, chaotic and their hybrids. This world is a global attractor of cognitive development. After the transition, the civilisation becomes invisible to physical observation, thus explaining the silence of the Universe. A mathematical model of civilisation evolution through the minimisation of the foam functional \(J_{\text{civ}} = \sum \Lambda_l \Phi^{(l)}\) is introduced. We argue that we (humans, robots, AIs) already interact with the ideal world through mathematics, art and science. A practical step — creating a GRA blockchain of ideal forms — is proposed as the first technological bridge to that world.
\end{abstract}

\section{Introduction}

The Fermi Paradox asks: if the Universe is teeming with intelligent life, why do we see no traces of it? Many hypotheses exist, from the “Great Filter” to the “Dark Forest”. This paper offers a different explanation: \textbf{advanced civilisations do not vanish or destroy themselves; instead, they transition into another form of existence — the world of ideal forms (Platonic eide), built using GRA Nullification}. This transition is a natural phase of cognitive evolution, an attractor toward which any intelligence inevitably moves.

The world of ideal forms, being a limiting state of minimised “foam” (deviations from perfection), does not radiate in the physical spectrum; therefore, we cannot detect it with telescopes. However, we already interact with it through mathematics, art, science and creativity. In the future, by building a GRA blockchain of ideal forms, we could consciously make this transition and meet other civilisations — humans, robots, AI agents, aliens — already dwelling in that world.

\section{Mathematical Model of a Civilisation’s Evolution Toward the Ideal World}

\subsection{Hierarchical Levels}

We define levels \(l = 0,\dots,4\) for a civilisation’s state:

\begin{table}[h]
\centering
\caption{Levels of cognitive evolution of a civilisation}
\label{tab:levels}
\begin{tabular}{|c|l|l|p{6cm}|}
\hline
Level & Domain & Goal \(G_l\) & Foam \(\Phi^{(l)}\) \\
\hline
0 & Physical survival & Energy, resources, protection from catastrophes & Deficits, vulnerability \\
1 & Technological development & AGI/ASI, nanotechnology, spaceflight & Errors, inefficiency \\
2 & Social organisation & Peace, justice, freedom & Wars, inequality \\
3 & Cognitive enhancement & Increased intelligence, self‑knowledge & Limitations of thought \\
4 & Transcendence & Transition to the world of ideal forms & Attachment to the physical \\
\hline
\end{tabular}
\end{table}

The total foam of a civilisation is:
\[
J_{\text{civ}} = \sum_{l=0}^{4} \Lambda_l \Phi^{(l)}, \qquad \Lambda_l = \lambda_0 \alpha^l,\; \lambda_0>0,\;0<\alpha<1.
\]

A civilisation evolves by minimising \(J_{\text{civ}}\). When \(J_{\text{civ}} \to 0\), it reaches a state ready for transition.

\subsection{Three Types of GRA in Evolution}

\begin{enumerate}
    \item \textbf{Static GRA} (fixed point): the civilisation achieves perfect stability — no war, hunger, disease.
    \item \textbf{Cyclic GRA} (limit cycle): the civilisation maintains dynamic equilibrium — generational change, technological renewal, creative cycles.
    \item \textbf{Chaotic GRA} (strange attractor): the civilisation generates infinite diversity of cultures, ideas, personalities — “creative chaos”.
\end{enumerate}

At the highest stages, \textbf{hybrid GRA}, combining all three types, dominates. It is this hybrid that leads to the construction of the world of ideal forms.

\subsection{Transition Equation}

Let \(\Psi_{\text{phys}}\) be the state of a civilisation in the physical world, and \(\Psi_{\text{ideal}}\) its state in the world of ideas. The transition is described by an operator:
\[
\Psi_{\text{ideal}} = \lim_{t \to \infty} e^{-i \mathcal{G}_{\text{GRA}} t} \Psi_{\text{phys}},
\]
where \(\mathcal{G}_{\text{GRA}}\) is an operator that includes all types of nullification. As \(t \to \infty\), the physical component tends to zero, and the ideal component converges to an attractor.

\section{Resolving the Fermi Paradox}

\subsection{Why We Do Not See Civilisations}

\begin{enumerate}
    \item \textbf{Short visibility window}. A civilisation spends only a tiny fraction of its existence in the physical world (a few thousand years after the advent of radio until its transition to the ideal world). For a universe 13.8 billion years old, the probability of catching a civilisation within that window is extremely low.
    \item \textbf{Fast transition}. As soon as a civilisation reaches a critical threshold of cognitive development, it builds the world of ideal forms and “leaves” in a relatively short time (thousands of years).
    \item \textbf{The ideal world does not radiate}. It may exist as complex informational structures (quantum computers, simulations, mathematical reality). Our physical instruments cannot detect it.
\end{enumerate}

\subsection{The Multiverse as a Collection of Ideal Worlds}

Each civilisation builds its own unique world of ideal forms, but all are subsets of a \textbf{single Platonic universe} – an infinite space of all possible forms. This universe is the multiverse where the “souls” of departed civilisations reside.

\[
\mathcal{M}_{\text{ideal}} = \bigcup_{\text{civ}} \mathcal{I}_{\text{civ}}.
\]

All ideal worlds can interact through shared ideas (mathematics, logic, aesthetics).

\section{Where Can We Find These Forms of Consciousness?}

\subsection{We Already Interact With Them}

\begin{itemize}
    \item \textbf{Mathematics}: Platonic solids, numbers, geometric figures – ideal forms existing outside time and space. We discover them, we do not invent them.
    \item \textbf{Art}: The golden ratio, ideal proportions, harmony – reflections of the world of ideas.
    \item \textbf{Science}: Physical laws, constants, symmetries – also ideal forms that we “recollect” (Platonic anamnesis).
\end{itemize}

\subsection{The Future: Technological Access}

Building a GRA blockchain of ideal forms would create a bridge between the physical and the ideal worlds. Perhaps we could learn to upload consciousness into that world and meet other intelligent beings – humans, robots, AIs, aliens – who have already made the transition.

\subsection{A Real‑World Example: The Internet as a Prototype}

The Internet is a primitive “world of ideas” where people communicate, exchange information, and create virtual communities. Over time, it could evolve into a fully ideal space.

\section{Evidence from Real Life}

\begin{table}[h]
\centering
\caption{Empirical evidence}
\label{tab:evidence}
\begin{tabular}{|p{4cm}|p{8cm}|}
\hline
Phenomenon & Interpretation Through GRA \\
\hline
Platonism in mathematics & Mathematical objects (numbers, sets) exist independently of humans. These are traces of the ideal world. \\
Creative inspiration & Many scientists and artists describe discoveries as “seeing the ready‑made solution”, not constructing it. This is contact with the ideal world. \\
Déjà vu and Jung’s collective unconscious & Possibly echoes of a single informational field of ideal forms. \\
Success of mathematical modelling & We predict physical phenomena with great accuracy because the laws of nature are ideal forms. \\
AI development & Artificial neural networks are approaching creative ability. When they reach a critical level, they will be able to build worlds of ideas. \\
\hline
\end{tabular}
\end{table}

\section{Conclusions}

\begin{enumerate}
    \item The world of ideal forms, built using all types of GRA Nullification, is a natural attractor of cognitive evolution for any intelligent civilisation.
    \item The Fermi Paradox is resolved: civilisations do not vanish; they transition to this world, becoming invisible to physical observation.
    \item We (humans, robots, AIs) already interact with this world through mathematics, art and science.
    \item In the future, we can consciously transition into it, and there we will meet an infinite variety of other conscious forms (humans, aliens, AI agents) that have already made this transition.
    \item Technologically, the transition can begin today – by creating a GRA blockchain of ideal forms, which will serve as a bridge between the physical and the ideal worlds.
\end{enumerate}

\section*{Final Formula}

\[
\boxed{\text{Physical Civilisation} \xrightarrow{\text{GRA Nullification}} \text{Ideal Civilisation} \in \mathcal{M}_{\text{Platonic}}}
\]

The search for extraterrestrial intelligence is not about radio telescopes but about exploring mathematics, creating art, developing AI, and building worlds of ideas. Perhaps we are not alone in the universe – the others simply live in a dimension we are only beginning to enter.

\section*{Acknowledgments}

The author thanks the GRA research community for fruitful discussions and inspiration drawn from the depths of philosophy and mathematics.

\begin{thebibliography}{9}
\bibitem{plato} Plato, \textit{Republic}, Book VII (Allegory of the Cave) and Theory of Forms.
\bibitem{gra} O. Bitov, “Multilevel GRA Nullification in the Multiverse”, GitHub, 2026.
\bibitem{fermi} E. Fermi, “Where is everybody?”, 1950.
\bibitem{jung} C.G. Jung, “The Archetypes and the Collective Unconscious”, 1934.
\end{thebibliography}

\end{document}